%-------------------------
% Resume in Latex
% Author : Zohair Khan
% Website: https://github.com/Zohair-Khan/resume
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \vspace{-2pt}\\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}



% Project Item
\newcommand{\projectItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

% Project Formatting
\newcommand{\resumeProjectSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} {#2} & \textit{\small#3} \\
    \end{tabular*}\vspace{-8pt}
}

% Achievement Formatting
\newcommand{\resumeAchievementSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} {#2} & \textbf{#3} \vspace{-2pt}\\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{-8pt}
}

% Relevant Coursework Formatting
\newcommand{\resumeCoursework}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \vspace{-2pt}\\
      {\small#2} \\
      {\small #3} \\
      {\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% %----------HEADING-----------------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{https://www.linkedin.com/in/khanzohair/}{\Large Zohair Khan}} & GitHub : \href{https://github.com/Zohair-Khan}{Zohair-Khan} \\
%   \href{mailto:zohairkhanmail@gmail.com}{zohairkhanmail@gmail.com} & LinkedIn: \href{https://www.linkedin.com/in/khanzohair/}{khanzohair}\\
%   +1-612-251-9420 \\ 
%   % \href{personal website link}{personal website} & Phone : +1-612-251-9420 \\
  
% \end{tabular*} 

\begin{center}
    \textbf{\Huge \scshape Zohair Khan} \\ \vspace{1pt}
    \textit {Motivated Senior CS Student looking for Software Engineering Internships} \\
    \href{mailto:zohairkhanmail@gmail.com}{\underline{zohairkhanmail@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/khanzohair/}{\underline{linkedin.com/in/khanzohair}} $|$
    \href{https://github.com/Zohair-Khan}{\underline{github.com/Zohair-Khan}} 
\end{center} 
\vspace{-21pt}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Metropolitan State University}{St. Paul, MN}
      {Bachelor of Science in Computer Science}{Expected Dec. 2024} \vspace{-5pt}
    \resumeCoursework
      {Relevant Coursework}
      {Computer Architecture \& Organization, Algorithms \& Data Structures, Object-Oriented Design \& Implementation,}
      {Database Management Systems, Networks \& Security, Organization of Programming Languages, Computational }
      {Linear Algebra, Discrete Mathematics, Probability \& Statistics, Technical Writing, Operating Systems (Spring 2024)}
  \resumeSubHeadingListEnd \vspace{-15pt}

%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Programming Languages:} {Proficient in Java, Python, C, C++. Entry-level HTML/CSS/JavaScript.} \\ \vspace{-5pt}
   }
   \item{
     \textbf{Databases:}{ Proficient with SQL, including MySQL and SQLite.} \\ \vspace{-5pt}
   }
   \item{
     \textbf{Software Development:}{ Version Control/Git, Unit Testing, Complexity Analysis, Technical Writing} \\ \vspace{-5pt}
   }
    \item{
     \textbf{Operating Systems:}{ Windows, Linux} \\ \vspace{-5pt}
   }
   \item{
     \textbf{Soft Skills:}{ Attention to Detail, Creative Problem Solving, Collaboration, Technical Communication} \\ \vspace{-1pt}
   }
   
 \resumeSubHeadingListEnd

 %-----------EXPERIENCE-----------------
\section{Experience} 
  \resumeSubHeadingListStart
    \resumeSubheading
      {Math \& ACT/SAT Prep Tutor}{Minneapolis, MN}
      {Self-Employed}{July 2020 - Present}
      \resumeItemListStart
        \projectItem
          {Providing personalized tutoring sessions to high school students in various math subjects, including Algebra, Geometry, Trigonometry, and Calculus, tailoring lessons to meet individual learning styles and needs.}
        \projectItem
          {Developing comprehensive ACT/SAT preparation plans, incorporating strategies, practice tests, and targeted review sessions to help students maximize their scores.}
        \projectItem
          {Demonstrating a strong ability to articulate complex technical concepts in a clear and concise manner, effectively communicating with students of varying backgrounds and skill levels.}
        \projectItem
          {Consistent track record of success in significantly raising students' grades and standardized test scores.}
      \resumeItemListEnd 
  \resumeSubHeadingListEnd 

%-----------Acheivements-----------------
\section{Achievements}
    \resumeSubHeadingListStart
        \resumeAchievementSubheading
          {CornHacks 2024}{\href{https://github.com/Zohair-Khan/CornHacks2024}{(GitHub)}}{2\textsuperscript{nd} Place}
          {Feb 2024}{Python, PyGame, MySQL}
          \resumeItemListStart
            \projectItem
              {Led a 4-person team comprised of undergraduate students from various academic years during a 24-hour hackathon, developing a PyGame-based roguelike game based on the hackathon's theme.}
            \projectItem
              {Applied object-oriented programming principles to architect and implement engaging gameplay elements.}
            \projectItem
              {Integrated a dynamic combat system, strategic power-ups, and a scoring mechanism, augmented by a SQL-powered leaderboard to foster competitive engagement.}
            \projectItem
              {Organized workflow efficiently, leveraging each team member's strengths to delegate tasks effectively and optimize productivity throughout the 24-hour development process.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Projects-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectSubheading
      {Decklist Auto-Filler Extension}{\href{https://chromewebstore.google.com/detail/decklist-auto-filler/knjanhkpoicpjebbkpcnbinkbdhhpfld}{(Chrome Web Store)}} {HTML, CSS, JavaScript}
      \resumeItemListStart
        \projectItem
          {Google Chrome extension for automatically migrating YuGiOh decklists from popular online simulators to tournament registration websites. \textbf{100+ daily users.}}
        \projectItem
          {Converts a Base64 encoded string into a list of card IDs, converts the IDs to card names, then seamlessly populates an HTML registration form with the card names.}
      \resumeItemListEnd
  
    \resumeProjectSubheading
      {Car Sales Application}{\href{https://github.com/Zohair-Khan/CarHub}{(GitHub)}} {Java, JavaFX/FXML, MySQL, Gradle}
      \resumeItemListStart
        \projectItem
          {Full-stack application for selling cars with a JavaFX/CSS front-end and Java back-end. MySQL database used with JDBC to store and manage all listing and user information, ensuring data integrity and reliability.}
        \projectItem
          {Implemented user authentication functionalities allowing users to log in and out, as well as create, delete, and view listings for cars.}
      \resumeItemListEnd

    \resumeProjectSubheading
      {Mock Bar Management Application}{\href{https://github.com/Zohair-Khan/Mock-Bar-Management-Application}{(GitHub)}} {Java, Swing, MySQL, Maven}
      \resumeItemListStart
        \projectItem
          {Full-stack application for managing a "mock" bar, with a Swing front-end and Java back-end.}
        \projectItem
          {JDBC used to perform CRUD operations on a MySQL database with bar-related data, including ingredients, suppliers, employees, and more.}
      \resumeItemListEnd
    
    \resumeProjectSubheading
      {Chat Room Application}{\href{https://github.com/Zohair-Khan/UDP-Socket-Chat}{(GitHub)}} {Python}
      \resumeItemListStart
        \projectItem
          {UDP socket based chat server and client program written in Python.}
        \projectItem
          {Server allows multiple clients to connect simultaneously and communicate with each other through public and direct messages.}
      \resumeItemListEnd

    \resumeProjectSubheading
      {TLS File Transfer Application}{\href{https://github.com/Zohair-Khan/TLS-File-Transfer}{(GitHub)}} {Python}
      \resumeItemListStart
        \projectItem
          {Secure file transfer application implementing TLS encryption to transfer files from a client to a host, written in Python.}
      \resumeItemListEnd


      

  \resumeSubHeadingListEnd



    

% %-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source python library for financial data analysis and machine learning for finance.}
%     \resumeSubItem{Github Visualization}
%       {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%     \resumeSubItem{Recommendation System}
%       {Music and Movie recommender systems using collaborative filtering on public datasets.}
% %     \resumeSubItem{Mac Setup}
% %       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%   \resumeSubHeadingListEnd

% %

\end{document}
